Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-12 Grassmannian_cells.tex
Testing \cH in Theorem 5.20

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\Gr_\bfe(P_{m+1})$ found in Theorem~\ref{celldec}.
In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ for truncated preprojectives $P_{m+1}^V$ are also naturally labeled by compatible pairs.
We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_{m+1}^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
\begin{theorem}
  \label{th:compatible cells}
  \sayD{Fix abuse of notation $H_m$.}
  For $m\ge1$ and $V\in\Gr(H_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
\end{theorem}
\begin{proof}
  The recursive construction of the 2-quivers $\cQ_{m+1}^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_{m+1}^{[r]}$.
  Indeed, when considering the recursive construction of the 2-quiver $Q_{m+1}^{[r]}$ from \eqref{eq:recursive 2-quivers}, we order the component quivers $Q_{m,i}$ and $Q_{m,*}^{[1]}$ naturally according to their indices so that $Q_{m,*}^{[1]}$ comes last.
  This provides a bijection of these vertices with the edges of $D_{m+1}^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges) of $D_{m+1}^{[r]}$.

>>>>

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

Our goal is to give a geometric explanation for this by showing that the compatible pairs provide a natural labeling for the cells of $\Gr_\bfe(P_{m+1})$ found in Theorem~\ref{celldec}.
In fact, we will see more: that the cells of quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ for truncated preprojectives $P_{m+1}^V$ are also naturally labeled by compatible pairs.
We accomplish this by providing a bijection between the compatible pairs as in Theorem~\ref{th:combinatorial euler} and the successor closed sets of vertices in the 2-quivers $\cQ_{m+1}^{[r]}$ used in Theorem~\ref{thm:2quivercells} to describe the nonempty cells.
\begin{theorem}
  \label{th:compatible cells}
  \sayD{Fix abuse of notation $H_m$.}
  For $m\ge1$ and $V\in\Gr(\cH_m)$ or $V=0$, each quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition with cells labeled by compatible pairs in the maximal Dyck path $D_{m+1}^{[r]}$, where $r=\dim V$.
\end{theorem}
\begin{proof}
  The recursive construction of the 2-quivers $\cQ_{m+1}^{[r]}$ provides a natural ordering of the vertices in the underlying quiver $Q_{m+1}^{[r]}$.
  Indeed, when considering the recursive construction of the 2-quiver $Q_{m+1}^{[r]}$ from \eqref{eq:recursive 2-quivers}, we order the component quivers $Q_{m,i}$ and $Q_{m,*}^{[1]}$ naturally according to their indices so that $Q_{m,*}^{[1]}$ comes last.
  This provides a bijection of these vertices with the edges of $D_{m+1}^{[r]}$ whereby vertices covering the vertex 1 (resp.\ vertex 2) of $K(n)$ correspond to horizontal edges (resp.\ vertical edges) of $D_{m+1}^{[r]}$.
